A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-17 paper.tex

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\renewcommand{\U}{\mathrm{U}}

@@

@@

\begin{example}
If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term. The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$. Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
\end{example}

@@

We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle. Consider the determinant map $\det\colon \U(n)\rightarrow \U(1)$. We define the unitary metalinear group to be
\[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
where $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.

@@

@@

\begin{prop} \label{CS_diml_red_prop}
Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
\end{prop}

\begin{proof}
We may assume $X,Y,M=\pt$ as in the previous proof.

We have
\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
and
\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
Under the pullback map
\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$. \brian{This is not defined} \chris{is compactly supported enough?  We want to compare pairings.}
\end{proof}

@@

Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and let $V=V_\RR\otimes_\RR\CC$ be its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

@@

\item A complex Lie group $G_R$, the \defterm{group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
\end{itemize}

@@

Let $A_\RR$ be a unital (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
\begin{enumerate}
\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.

\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
\end{enumerate}

In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e. $A_\RR$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.

For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries. We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$. $V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$. Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.

We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$. So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.

@@

We will be interested in the following examples:
\begin{enumerate}
\item (\textbf{3d $\mc N=1$ supersymmetry}) $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$.

\item (\textbf{4d $\mc N=1$ supersymmetry}) We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$. Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations. We have two choices: $A_\RR=\CC$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR=\RR[x]/(x^2-1)$ is the algebra of split-complex numbers (which equips $V_\RR$ with a metric of split signature (2, 2)).

\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator. Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$. We have two choices: $A_\RR = \mathbb{H}$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-quaternions (which equips $V_\RR$ with a metric of split signature $(3, 3)$).

\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation. We have two choices: $A_|RR$ is the algebra of octonions (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-octonions (which equips $V_\RR$ with a metric of split signature $(5, 5)$).
\end{enumerate}

@@

\begin{definition}
A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
\end{definition}

It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$. We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
\begin{itemize}
\item A supercharge $Q$ is \defterm{topological} if $d = n$.

@@

We will now define the twist of a supersymmetric field theory by a square-zero supercharge.  In order to obtain a $\ZZ$-graded theory, we will need to also include an additional piece of data as follows.

\begin{definition}
A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
\end{definition}

Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
Recall from Section \ref{symmetry_section} that this means we have a Maurer-Cartan element 
\[
I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
\]
where $I_{\fA}^{(k)} \colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
Define
\[
I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
\]
Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.

\begin{definition} \label{def:twisting}
Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The {$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{I_{\fA}^2(Q), -\}, \omega, I + I_{\fA}^{\ge 3}(Q))$, where
\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
\end{definition}

\begin{prop}
The collection $\left(E^Q, Q_{\mr{BV}} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
\end{prop}

\begin{proof}
The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.

Ellipticity of $(E^Q, \d + \{I_\fA^2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
The operator 
\end{proof}

\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}

\begin{remark}
Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2\ZZ$-graded classical field theory
\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
where the $\ZZ/2\ZZ$-grading on $E$ is the total grading.
\end{remark}

@@

\subsection{Twisting Homomorphisms and Curved Backgrounds}

@@

\item A ghost field $c\in\Gamma(V_\RR; \fg[1])$.
\end{itemize}
We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
Let $\cE_{\rm Super Yang-Mills}$ denote the space of BV fields.

@@

We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. 
Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, with $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$. The action of supersymmetry is given by a linear and a quadratic functional
\begin{align*}
I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \\
I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
\end{align*}

The following theorem summarizes the fact that super Yang-Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.

\begin{thm}\label{thm:gaugemultipletSUSY}
The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm Super Yang-Mills}))$ satisfies the classical master equation
\[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
\end{thm}

@@

Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}. In addition, fix a real associative composition algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and denote its complexification by $A$. Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure. Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}. We make the following additional assumption.

@@

Explicitly, we consider the following cases:
\begin{itemize}
\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{3d $\cN=1$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.

\item (\textbf{4d $\cN=1$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.

\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
\end{itemize}

Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
\[(av, w) = (v, \sigma(a)w).\]
Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing. Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
\begin{itemize}
\item $A_\RR=\RR$, so $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.

\item $A_\RR=\CC$, so $A=\CC[x]/(x^2+1)$. A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$. Note that with respect to the right $A$-action $x$ acts as $\mp i$ on $P_{\pm}$. So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$. In other words, the data boils down to a $\fg$-representation $R$, so that $P = R\oplus R^*$.

>>>>

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\Hod}{\mathrm{Hod}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\renewcommand{\U}{\mathrm{U}}

@@

\pavel{We need to introduce classical field theories linear over a commutative ring (used to talk about symmetries and the Hodge family).}

@@

\begin{example}
If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term. The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$. Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
\label{ex:CSBF}
\end{example}

@@

We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle. We define the unitary metalinear group to be
\[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
where $\U(n)\rightarrow \U(1)$ is the determinant map and $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.

@@

\subsubsection{Generalized Hodge theory}

We will also consider deformations of the generalized BF theory to a perturbatively trivial theory. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

Given an $L_\infty$ algebra $\fg$ we denote by $\fg_{\Hod}$ the $\CC[t]$-linear $L_\infty$ algebra
\[\fg_{\Hod} = \CC[t]\otimes (\fg\oplus \fg[1])\]
with the $L_\infty$ brackets coming from the $L_\infty$ brackets on $\fg$ in the first term, where we consider $\fg[1]$ as the adjoint representation of $\fg$. The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.

If $\fg$ carries a nondegenerate invariant symmetric paiirng of degree $d$, so does $\fg_{\Hod}$.

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
\end{definition}

\begin{prop}
The $t=0$ specialization of the generalized Hodge theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.

The specialization of the generalized Hodge theory at $t\neq 0$ is perturbatively trivial.
\label{prop:Hodgetheoryspecialization}
\end{prop}
\begin{proof}
At $t=0$ we get
\[\left.\fg_\Hod\right|_{t=0}\cong \fg\oplus \fg[1]\cong \fg\oplus \fg^*[d-1],\]
where we use the symmetric bilinear pairing on $\fg$ in the second isomorphism. The first claim then follows from Example \ref{ex:CSBF}.

At $t\neq 0$ the $L_\infty$ algebra $\fg_\Hod$ becomes acyclic which proves the second claim.
\end{proof}

@@

Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and an orientation. Recall that the symmetric bilinear pairing trivializes $\det(V_\RR)^{\otimes 2}$ and the orientation allows us to obtain a trivialization of $\det(V_\RR)$, i.e. a real volume form. We denote by $V=V_\RR\otimes_{\RR}\CC$ its complexification. $V$ inherits a nondegenerate Hermitian form from the symmetric bilinear pairing on $V_\RR$. Moreover, $V$ carries a complex volume form $\Omega_V$:
\[\det(V)\cong \det(V_\RR)\otimes_{\RR}\CC\]
and we use the real volume form on $V_\RR$.

Functoriality of this construction gives a group homomorphism
\begin{equation}
\SO(V_\RR)\longrightarrow \SU(V)
\label{eq:SOtoSU}
\end{equation}
such that the real projection $\Re\colon V\rightarrow V_\RR$ is $\SO(V_\RR)$-equivariant.

\begin{prop} \label{CS_diml_red_prop}
Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above. Consider the generalized Chern--Simons theory
\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
The isomorphism is moreover $\SO(V_\RR)$-equivariant.
\end{prop}
\begin{proof}
We may assume $X,Y,M=\pt$ as in the previous proof.

We have
\[\Omega^{0, \bullet}_V\cong \Sym_\CC^\bullet(\underline{V}[-1])\]
and
\[\Omega^\bullet_{V_\RR}\cong \Sym_\RR^\bullet(\underline{V}_\RR[-1])\otimes_\RR\CC.\]

Under the pullback map
\[\Omega^\bullet(V_\RR; \CC)\rightarrow \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
the integration map $\int_V \Omega_V\wedge (-)\colon \Omega^{0, \bullet}(V)\rightarrow \CC$ reduces to the integration map $\int_{V_\RR} (-)\colon \Omega^{\bullet}(V_\RR;\CC)\rightarrow \CC$. \brian{This is not defined} \chris{is compactly supported enough?  We want to compare pairings.}
\end{proof}

@@

Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a nondegenerate symmetric bilinear form. Denote by $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

@@

\item A Lie group $G_R$, the \defterm{group of $R$-symmetries}, which acts on $\Sigma$ by $\so(V)$-equivariant automorphisms preserving $\Gamma$.
\end{itemize}

@@

Let $A$ be a unital (possibly non-associative) complex algebra equipped with an antiinvolution $\sigma\colon A\rightarrow A$. We make the following assumptions:
\begin{enumerate}
\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A$ spanned by the unit.

\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A\rightarrow \CC$. We assume that it is nondegenerate.
\end{enumerate}

In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e. $A$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.

For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries. We define $V$ to be the space of $2\times 2$ Hermitian matrices with values in $A$, so that $\dim(V) = \dim(A) + 2$. $V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$. Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.

@@

We will be interested in the following examples:
\begin{enumerate}
\item (\textbf{3d $\mc N=1$ supersymmetry}) $A = \CC$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3, \CC)$.

\item (\textbf{4d $\mc N=1$ supersymmetry}) $A = \CC\otimes_{\RR}\CC\cong \CC[x]/(x^2+1)$ with $\sigma(x) = -x$. Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.

\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator. Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.

\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{O}\otimes_{\RR}\CC$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
\end{enumerate}

@@

\begin{definition}
A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$. Its \defterm{number of invariant directions} is the dimension of the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$.
\end{definition}

It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the number $d$ of invariant directions is at least $n/2$. We will use the following adjectives for square-zero supercharges depending on $d$:
\begin{itemize}
\item A supercharge $Q$ is \defterm{topological} if $d = n$.

@@

Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
\[
I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
\]
where $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.

\begin{definition} \label{def:twisting}
Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge. The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
\[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
\end{definition}

Given additional data, we may enhance the classical field theory.

\begin{definition}
Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1.
\end{definition}

Given a homomorphism $\alpha$, we consider the new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$. The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-grading $k$. But it also has cohomological degree $-k$. In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.

\begin{definition}
Let $Q\in\Sigma$ be a square-zero supercharge and suppose $G\rightarrow \Spin(V_\RR)$ is a fixed group homomorphism. A \defterm{twisting homomorphism} is a homomorphism $\phi\colon G\rightarrow G_R$ such that $Q$ is preserved under the composite $G\rightarrow \Spin(V_\RR)\times G_R$.
\end{definition}

The classical field theory $(E, S, \omega)$ carries a $\Spin(V_\RR)\times G_R$-action. However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $I_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$. However, given a twisting homomorphism $\phi$ we see that $I_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.

@@

@@

\item A ghost field $c\in\Gamma(V_\RR; \fg[1])$.
\end{itemize}

We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$. Let $\cE_{\gauge}$ denote the space of BV fields.

@@

We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$. The action of supersymmetry is given by a linear and a quadratic functional
\begin{align}
I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right). \label{eq:gaugeI2}
\end{align}

The following theorem summarizes the fact that super Yang--Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.

\begin{thm}\label{thm:gaugemultipletSUSY}
The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
\[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric.  
\end{thm}

@@

Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}. In addition, fix a complex associative composition algebra $A$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras}. Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure. Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}. We make the following additional assumption.

@@

Explicitly, we consider the following cases:
\begin{itemize}
\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A = \CC[x]/(x^2+1)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A = \eend(W_+)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{3d $\cN=1$ supersymmetry}) $A = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.

\item (\textbf{4d $\cN=1$ supersymmetry}) $A = \CC[x]/(x^2+1)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.

\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A = \eend(W_+)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
\end{itemize}

Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
\[(av, w) = (v, \sigma(a)w).\]
Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing. Explicitly, for $A=\CC, \CC\otimes_\RR\CC, \mathbb{H}\otimes_\RR\CC$ we get the following data:
\begin{itemize}
\item $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.

\item $A=\CC[x]/(x^2+1)$. A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$. Note that with respect to the right $A$-action $x$ acts as $\mp i$ on $P_{\pm}$. So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$. In other words, the data boils down to a $\fg$-representation $R$, so that $P = R\oplus R^*$.
